### 2023-09-02 sections/4-results.tex
bruteforce-blass benchmarks

    \textbf{Dataset} & \textbf{Dist.}  &\textbf{Card.}  & \textbf{Dim.}  & \textbf{k}  & \multicolumn{2}{r}\textbf{faiss-ivf} & \multicolumn{2}{r}\textbf{redisearch} & \multicolumn{2}{r}\textbf{hnsw(faiss)} & \multicolumn{2}{r}\textbf{CAKES} \\

@@

    nytimes          & cos              & 290,000            & 256             & 10         & 0.69 &  1413.35                       & 0.90 & 616.21                            & 0.97 & 92.92                                         & 1.00 & 42 \\

@@

    nytimes          & cos              & 290,000            & 256             & 100        & 0.61 &  0.71                          & 0.50 & 0.45                              & 0.00 & 0.00                                          & 1.00 & 42 \\

@@

    fashion-mnist    & euc              & 60,000	         & 784            & 10         & 0.54 & 324.79                           & 0.99 & 444.89                                  & 0.94 & 60.89                                                    & 1.00 & 42 \\

@@

    fashion-mnist    & euc              & 60,000             & 784            & 100        & 1.00 & 111.47                           & 0.50 & 0.49                                  & 0.99 & 277.80                                                    & 1.00 & 42 \\

@@

    gist             & euc              & 1,000,000          & 960             & 10         & 1.00 & 3.55                           & -- & --                                     & 0.95 & 149.58                                                   & 1.00 & 42 \\

@@

    gist             & euc              & 1,000,000          & 960             & 100        & 1.00 & 2.70                           & 0.68 & 0.47                                 & 0.99 & 59.71                                                    & 1.00 & 42 \\

@@

    glove-25         & cos              & 1,183,514          & 25             & 10         & 1.00 & 78.78                          & 1.00 & 37.85                               & 1.00 & 552.67                                                  & 1.00 & 42 \\

@@

    glove-100        & cos              & 1,183,514          & 100            & 10         & 1.00 & 21.16                          & 0.99 & 133.05                                & 0.99 & 155.90                                                  & 1.00 & 42 \\

@@

    glove-100        & cos              & 1,183,514          & 100            & 100        & 0.99 &  19.04                          & -- & --                                  & 0.99 & 92.58                                                    & 1.00 & 42 \\

@@

    sift             & euc              & 1,000,000          & 128            & 10         & 1.00 &  24.52                          & 1.00 & 505.79                               & 1.00 & 275.07                                                    & 1.00 & 42 \\

@@

    sift             & euc              & 1,000,000          & 128            & 100        & 1.00 &  23.50                          & 0.50 & 0.45                                  & 0.99 & 179.14                                                    & 1.00 & 42 \\

>>>>

    \textbf{Dataset} & \textbf{Dist.}  &\textbf{Card.}  & \textbf{Dim.}  & \textbf{k}  & \multicolumn{2}{r}\textbf{faiss-ivf} & \multicolumn{2}{r}\textbf{bruteforce-blas} & \multicolumn{2}{r}\textbf{hnsw(faiss)} & \multicolumn{2}{r}\textbf{CAKES} \\

@@

    nytimes          & cos              & 290,000            & 256             & 10         & 0.69 &  1413.35                       & 0.99 & 26.66                            & 0.97 & 92.92                                         & 1.00 & 42 \\

@@

    nytimes          & cos              & 290,000            & 256             & 100        & 0.61 &  0.71                          & 0.99 & 10.71                              & 0.00 & 0.00                                          & 1.00 & 42 \\

@@

    fashion-mnist    & euc              & 60,000	         & 784            & 10         & 0.54 & 324.79                           & 1.00 & 52.91                                  & 0.94 & 60.89                                                    & 1.00 & 42 \\

@@

    fashion-mnist    & euc              & 60,000             & 784            & 100        & 1.00 & 111.47                           & 0.99 & 16.02                                  & 0.99 & 277.80                                                    & 1.00 & 42 \\

@@

    gist             & euc              & 1,000,000          & 960             & 10         & 1.00 & 3.55                           & 1.00 & 2.63                                     & 0.95 & 149.58                                                   & 1.00 & 42 \\

@@

    gist             & euc              & 1,000,000          & 960             & 100        & 1.00 & 2.70                           & 0.99 & 0.80                                 & 0.99 & 59.71                                                    & 1.00 & 42 \\

@@

    glove-25         & cos              & 1,183,514          & 25             & 10         & 1.00 & 78.78                          & 1.00 & 33.52                              & 1.00 & 552.67                                                  & 1.00 & 42 \\

@@

    glove-100        & cos              & 1,183,514          & 100            & 10         & 1.00 & 21.16                          & 1.00 & 16.52                                & 0.99 & 155.90                                                  & 1.00 & 42 \\

@@

    glove-100        & cos              & 1,183,514          & 100            & 100        & 0.99 &  7.52                          & 0.99 & 3.11                                  & 0.99 & 92.58                                                    & 1.00 & 42 \\

@@

    sift             & euc              & 1,000,000          & 128            & 10         & 1.00 &  24.52                          & 1.00 & 16.40                               & 1.00 & 275.07                                                    & 1.00 & 42 \\

@@

    sift             & euc              & 1,000,000          & 128            & 100        & 1.00 &  23.50                          & 1.00 & 6.51                                  & 0.99 & 179.14                                                    & 1.00 & 42 \\
